\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Tehran Institute for Advanced Studies (TeIAS)}{January 2022 - Now}
{Research Experience}{January 2022 - Now}
\resumeItemListStart
\resumeItem{Research Assistant at \textbf{TeIAS (HCI, Vision and Blockchain)} - {Under supervision of Dr. Alipour}}
\resumeItem{I participate in research activities in HCI, Vision and Blockchain under the supervision of Dr. Sharareh Alipour. We've worked on two Vision and HCI-based papers, which both have got submitted to CHI 2023 and WWW 2023. Our primary research ideas are Vision, HCI, and AI-based, and in the last project, we worked on a fashion recommender system.}
    \resumeItem{I am implementing a Blockchain-based education website, using Django for Backend API, React for Frontend design and Docker.}
\resumeItemListEnd
\vspace*{-0.05cm}

\resumeSubheading
{Institute for Research in Fundamental Sciences (IPM)}{January 2022 - Now}
{Research Experience}{January 2022 - Now}
\resumeItemListStart
\resumeItem{Research Assistant at \textbf{IPM (HCI and Blockchain)} - {Under supervision of Dr. Alipour}}
\resumeItem{I participated in research activities in HCI and Blockchain under the supervision of Dr. Sharareh Alipour. As a result, we got a bronze medal at IBCOL 2022 and a gold medal at the national blockchain olympiad.}
%\resumeItem{I am implementing a Blockchain-based education website, using Django for Backend API, React for Frontend design and Docker.}
\resumeItemListEnd
\vspace*{-0.05cm}

\resumeSubheading
{Sharif University of Technology}{September 2020 -- Now}
{Teaching Experience}{Fall 2021 - Now}
\resumeItemListStart
\resumeItem{Head Teaching Assistant - \textbf{Numerical Computations} -  Dr. Hossein Ghorban, Dr. Hamid Sarbazi Azad - Spring 2023}
\resumeItem{Head Teaching Assistant - \textbf{Numerical Computations} -  Dr. Hossein Ghorban, Dr. Hamid Sarbazi Azad - Fall 2022}
\resumeItem{Teaching Assistant - \textbf{Probability and Statistics for Engineering} -  Dr. Jafari - Spring 2023}
\resumeItem{Teaching Assistant - \textbf{Probability and Statistics for Engineering} -  Ms. Manifi - Spring 2023}
\resumeItem{Teaching Assistant - \textbf{Linear Algebra} -  Dr. Hossein Ghorban - Spring 2023 \& Spring 2022 \& Fall 2022}
\resumeItem{Teaching Assistant - \textbf{Compiler Design} - Ms. Hosseinmardi - Spring 2023}
\resumeItem{Teaching Assistant - \textbf{Computer Architecture} -  Dr. Laleh Arshadi - Spring 2023 \& Fall 2022}
\resumeItem{Teaching Assistant - \textbf{Data Structures and Algorithms} -  Dr. Safarnezhad - Spring 2022 \& Fall 2022}
\resumeItem{Teaching Assistant - \textbf{Object Oriented Programming} -  Dr. Bizhan Vosoughi \& Dr. Matin Hashemi - Spring 2022}
\resumeItem{Teaching Assistant - \textbf{Advanced Programming in Java} -   Dr. MohammadAmin Fazli - \footnotesize{Spring 2023 \& Spring 2022}}
\resumeItem{Teaching Assistant - \textbf{Advanced Programming in Java} -  Mr. Vahid Salmani - Fall 2021}
\resumeItem{Teaching Assistant - \textbf{Mobile Programming} -   Mr. Nari - \footnotesize{Spring 2023}}
\resumeItem{Head Teaching Assistant - \textbf{Fundamentals of Programming in C} -  Dr. MohammadAmin Fazli - Fall 2022}
\resumeItem{Head Teaching Assistant - \textbf{Fundamentals of Programming C} -  Mr. AliReza Golmohammadi - Spring 2022}
\resumeItem{Head Teaching Assistant - \textbf{Fundamentals of Programming C} -  Mr. Milad Raeisi - Spring 2022}
\resumeItem{Co-Head Teaching Assistant - \textbf{Fundamentals of Programming C} -  Dr. MohammadAmin Fazli - Fall 2022}
\resumeItem{Co-Head Teaching Assistant - \textbf{Fundamentals of Programming C} -  Mr. Hosseinkhani - Spring 2023}
\resumeItem{Teaching Assistant - \textbf{Fundamentals of Programming C} -  Dr. MohammadAmin Fazli - Fall 2021}
\resumeItem{Teaching Assistant - \textbf{Fundamentals of Programming C} -  Mr. Poursoltani - Spring 2023}
\resumeItem{Teaching Assistant - \textbf{Fundamentals of Programming Python} -  Mr. Alireza Aghamohammadi - Spring 2022}
\resumeItem{Teaching Assistant - \textbf{Fundamentals of Programming Python} -  Mr. Shahraki - Spring 2023}
\resumeItem{Teaching Assistant - \textbf{Fundamentals of Programming Python} -  Mr. Turaj Arminpour - Spring 2022}
\resumeItem{Teaching Assistant - \textbf{Fundamentals of Programming Python} -  Ms. Nafari - Spring 2022}
\resumeItem{Teaching Assistant - \textbf{Logic Design} -  Dr. Laleh Arshadi - Spring 2023}


%	\vspace*{-0.5cm}





%	\vspace*{-0.5cm}









%	\vspace*{-0.5cm}







%	\vspace*{-0.5cm}




\resumeItemListEnd
\vspace*{-0.15cm}
\resumeSubheading
{Micromaster}{August 2022 - Now}
{Co-Founder}{}
\resumeItemListStart
\resumeItem{Micromasters programs are a series of master-level courses from the Sharif University of Technology with a vision of providing life-transforming،, high-quality learning experiences to enthusiastic learners around the country.}
\resumeItem{Worked on an education platform using Javascript, React, PHP, Postgres, and Docker. I also managed the system and a team of 30 people working for the company.}
\resumeItemListEnd

\vspace*{-0.15cm}
\resumeSubheading
{Guardian}{August 2022 - Now}
{Frontend Developer}{}
\resumeItemListStart
\resumeItem{worked on an application that could detect car accidents and communicate with all the passengers and drivers to help prevent crashes using React.js, JavaScript, HTML, and CSS.}
\resumeItemListEnd

\resumeSubHeadingListEnd